---
title: "Logistic Growth Model in R"
author: "Siddharth Namachivayam"
date: "3/14/2019"
output: html_document
---
<style>
body {
    background-color: #FFEDBA;
}

div.center {
  text-align: center;
}

.caption {
    font-size: x-small;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<div class="center">
## Background
</div>

In future posts, I assume that I will have to quite frequently analyze and plot various differential equations along with their solution curves and orbits. So, in this post, I want to provide readers a basic introduction to analyzing and plotting differential equations in R by looking at the logistic growth model. 

To solve and plot differential equations, I used the following packages installed from RStudio:
<br>
1) deSolve
<br>
2) rootSolve
<br>
3) bvpSolve
<br>
4) ReacTran
<br>
5) simecol

I presume that these packages use relatively simple numerical methods for their solvers, but nevertheless they should suffice for the purposes of this blog (i.e. provide some nice plots).

<div class="center">
## The Logistic Growth Model
</div>

```{r lead_system}
library(deSolve)
leadi=function(t,y,parms)
{
  dy1=-0.0361*y[1]+0.0124*y[2]+0.000035*y[3]+49.3
  dy2=0.0111*y[1]-0.0286*y[2]
  dy3=0.0039*y[1]-0.000035*y[3]
  list(c(dy1,dy2,dy3))
}
yini=c(y1=0,y2=0,y3=0)
times=seq(0,400,0.1)
out=ode(times=times,y=yini,func=leadi,parms=NULL)
plot(out)
thing=data.frame(out)
index=match(400,data.frame(out)$time)
max=data.frame(out)$y3[index]
lead=function(t,y,parms)
{
  dy1=-0.0361*y[1]+0.0124*y[2]+0.000035*y[3]
  dy2=0.0111*y[1]-0.0286*y[2]
  dy3=0.0039*y[1]-0.000035*y[3]
  list(c(dy1,dy2,dy3))
}
yini=c(y1=thing$y1[index],y2=thing$y2[index],y3=thing$y3[index])
times=seq(0,100000,0.1)
kout=ode(times=times,y=yini,func=lead,parms=NULL)
plot(kout)
vals=data.frame(kout)$y3
pol=NULL
for(val in vals)
{
  if(val<max*0.1)
  {
    pol=val
    break
  }
}



ni=match(pol,data.frame(kout)$y3)
data.frame(kout)$time
tlk=data.frame(kout)$time[ni]
tlk
```
Create function to go through vals and find when first <.5*2215.886


